Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry

### 2017-09-21 pre_post.tex
Fix kinship issue

In overview, each model generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation. Offspring inherit a randomly sampled allele from each parent at each locus. Alleles can then mutate and offspring express inbreeding depression in viability. Immigrants arrive in the population and density regulation limits population growth (see below). We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted. Key individual traits, parameter values, and variables are described in Table 1.

@@

>>>>

In overview, each model generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation. Offspring inherit a randomly sampled allele from each parent at each locus. Alleles can then mutate and offspring express inbreeding depression in viability. Immigrants arrive in the population and density regulation limits population growth (see below). We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent, \textcolor{blue}{therefore ranging from 0-1}), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted. \textcolor{blue}{Values of $k$ are calculated directly from the pedigree using a standard iterative algorithm \cite[e.g.,][]{Boyce1983, Duthie}}. Key individual traits, parameter values, and variables are described in Table 1.

@@

\bibitem[{Boyce(1983)}]{Boyce1983}
Boyce, A. 1983.
\newblock {Computation of inbreeding and kinship coefficients on extended pedigrees}
\newblock \textit{J. Hered.} \textbf{74}:400--404.
